An elaborate data set on human gait and the effect of mechanical perturbations

### 2015-01-14 paper.tex
Accentuate Figures 2 and 3 in the text, fixes #92
Moved the subject of the sentence, the figures, to the beginning of the
paragraphs.

The MATLAB script and Simulink model produce a comma-delimited text file of
five desired belt speed signals indexed by the time stamp. There are slow, normal,
and fast walking speeds and slow and fast running speeds.~\footnote{The running
signals were not used in the experiments presented in this paper.} The measured
speed of the treadmill belts from unloaded trials (79, 80, 81) are compared to
the commanded treadmill control input signals in
Figure~\ref{fig:input_output} to show the effect of the treadmill and
controller dynamics. The system introduces a delay and seems to act as a low
pass filter. The standard deviations of the measured speeds do not
significantly differ from the desired values:
\SIlist{0.05;0.12;0.2}{\meter\per\second} for the three speeds, respectively.
%
\begin{figure}
  \centering
  \includegraphics{figures/input_vs_output.pdf}
  \caption{Commanded treadmill belt speed (red) and the recorded
    speed (blue) for average belt speeds of
    \SIlist{0.8;1.2;1.6}{\meter\per\second}, respectively.}
  \label{fig:input_output}
\end{figure}

To show the effects of the treadmill dynamics and give an idea of the frequency
content of the actual perturbations, spectral density plots were created
by averaging a spectrogram of a twenty second Hamming window, shown
in Figure~\ref{fig:freq_analysis}. For all speeds, the frequency content of the
commanded and measured time series show similarity below 4~\si{\hertz} and
attenuation in the measured spectral density above 4~\si{\hertz}.
%
\begin{figure}
  \centering
  \includegraphics{figures/frequency_analysis.pdf}
  \caption{Power spectral density of the commanded treadmill belt speed
    (red) and the recorded speed (blue) for average belt speeds of
    \SIlist{0.8;1.2;1.6}{\meter\per\second}, respectively}
  \label{fig:freq_analysis}
\end{figure}

>>>>

The MATLAB script and Simulink model produce a comma-delimited text file of
five desired belt speed signals indexed by the time stamp. There are slow, normal,
and fast walking speeds and slow and fast running speeds.~\footnote{The running
signals were not used in the experiments presented in this paper.}

Figure~\ref{fig:input_output} gives an idea of the effect of the treadmill and
controller dynamics by plotting the measured speed of the treadmill belts from
unloaded trials (79, 80, 81) against the commanded treadmill control input
signal. The system introduces a delay and seems to act as a low pass filter.
The standard deviations of the measured speeds do not significantly differ from
the desired values: \SIlist{0.05;0.12;0.2}{\meter\per\second} for the three
speeds, respectively.
%
\begin{figure}
  \centering
  \includegraphics{figures/input_vs_output.pdf}
  \caption{Commanded treadmill belt speed (red) and the recorded
    speed (blue) for average belt speeds of
    \SIlist{0.8;1.2;1.6}{\meter\per\second}, respectively.}
  \label{fig:input_output}
\end{figure}

Figure~\ref{fig:freq_analysis} gives a frequency domain view of the effects of
the treadmill dynamics. These spectral density plots were created by averaging
a spectrogram of a twenty second Hamming window. For all speeds, the frequency
content of the commanded and measured time series show similarity below
4~\si{\hertz} and attenuation in the measured spectral density above
4~\si{\hertz}.
%
\begin{figure}
  \centering
  \includegraphics{figures/frequency_analysis.pdf}
  \caption{Power spectral density of the commanded treadmill belt speed
    (red) and the recorded speed (blue) for average belt speeds of
    \SIlist{0.8;1.2;1.6}{\meter\per\second}, respectively}
  \label{fig:freq_analysis}
\end{figure}
